Temporal Developer Concept Witchery: Latent Dirichlet Allocation Applied to Revisions

### 2009-02-18 presentation/presentation.out.tex
plots added

\documentclass[titlepage,usenames,a4,landscape,semhelv]{seminar}
\newcommand{\presenter}{Abram Hindle}
\newcommand{\conference}{}
\newcommand{\gettitle}{Temporal Developer Concept Witchery: Latent Dirichlet Allocation Applied to Revisions}

@@

\end{itemize}
\sslide{Topic Clustering }
\begin{itemize}
\item Need to track continuous topics across 
\item Similarity between topics
\item Clusters of the transitive closure of topics with X\% similarity
	\begin{itemize}
	\item Fill flood along similarity, make subsets of everyone who X\% similar to any of their neighbors, make that a cluster

@@

@@

\end{itemize}
\end{itemize}
\end{slide}

>>>>

\documentclass[titlepage,usenames,a4,landscape,semhelv,16pt]{seminar}
\newcommand{\presenter}{Abram Hindle}
\newcommand{\conference}{}
\newcommand{\gettitle}{Temporal Developer Concept Witchery: Latent Dirichlet Allocation Applied to Revisions}

@@

\end{itemize}
\sslide{Dictionary}
\begin{itemize}
\item Message - in this a CVS Commit
\item Word Distribution - count of words occuring in a message
\item Topic - a word distribution that is common amongst messages
\item Trend - a topic that re-occurs

\newslide
\igbigcapb{commit-to-topics}{How commits are aggregated into Topics}

\end{itemize}
\sslide{Developer Trends}
\begin{itemize}
\item Trends
	\begin{itemize}
	\item Continuous or repeating topics
	\item Occur over multiple time windows

\end{itemize}
\end{itemize}
\sslide{Topic Similarity}
\begin{itemize}
\item Given 2 topics
	\begin{itemize}
	\item if their top 10 words 
		\begin{itemize}
		\item share X words (7 or more)
			\begin{itemize}
			\item they are similar

		\end{itemize}
	\end{itemize}
\end{itemize}
\end{itemize}
\sslide{LDA}
\begin{itemize}
\item Latent Dirichlet Allocation
\item Like Latent Semantic Indexing (LSI)
\item Like ICA/PCA
\item Black box view:
	\begin{itemize}
	\item Input word distributions of messages, 
	\item Output topics consisting of a word distribution and related messages

\end{itemize}
\end{itemize}
\sslide{Topic Clustering }
\begin{itemize}
\item Need to track continuous topics across 
\item Similarity between topics
\item Clusters of the transitive closure of topics with X\% similarity
	\begin{itemize}
	\item Fill flood along similarity, make subsets of everyone who X\% similar to any of their neighbors, make that a cluster

@@

\end{itemize}
\end{itemize}
\sslide{Case Study: Portability}
\begin{itemize}
\item MySQL 3.23 
	\begin{itemize}
	\item Discussions relating to portability
	\item Some topics smeared across multiple months

@@

\end{itemize}
\end{itemize}
\sslide{Observations}
\begin{itemize}
\item Topics could be named
	\begin{itemize}
	\item Certain words indicate a focus on
		\begin{itemize}
		\item Maintenance
		\item Bug Fixing
		\item Portability
		\item Potential 'ilities

	\end{itemize}
\end{itemize}
\end{itemize}
\sslide{Observations}
\begin{itemize}
\item Powerlaw distribution of repeating topic counts
	\begin{itemize}
	\item Most occured once
	\item A few were repeated 
		\begin{itemize}
		\item less than 10\% of topics reoccur

	\end{itemize}
\end{itemize}
\end{itemize}
\sslide{Unfinished}
\begin{itemize}
\item Total Topics versus Monthly Topics

\end{itemize}
\sslide{Future work}
\begin{itemize}
\item Extension, associate Trends or Topics with purpoes by using wordnet and Taxonomies of software quality

\end{itemize}
\end{slide}

### 2009-02-18 presentation/presentation.tex
plots added

@@

@@

>>>>

\newslide
\igbigcapb{commit-to-topics}{How commits are aggregated into Topics}

=Developer Trends
* Trends
** Continuous or repeating topics
** Occur over multiple time windows

=Topic Similarity
* Given 2 topics
** if their top 10 words 
*** share X words (7 or more)
****  they are similar

=LDA
* Latent Dirichlet Allocation
* Like Latent Semantic Indexing (LSI)
* Like ICA/PCA
* Black box view:
** Input word distributions of messages, 
** Output topics consisting of a word distribution and related messages

@@

=Case Study: Portability
* MySQL 3.23 
** Discussions relating to portability
** Some topics smeared across multiple months

@@

\igbigthirtyfivecapb{fixed-time-smear-plot-cropped}{}
\igbigthirtyfivecapb{fixed-time-smear-plot-scaled}{}

\igbigthirtyfivecapb{histogram-cropped}{}
\igbigthirtyfivecapb{histogram-cropped-scaled}{}

%class-smear-plot-crop

\igbigthirtyfivecapb{class-smear-plot-crop-scaled}{}         
\igbigthirtyfivecapb{class-smear-plot-crop-scaled-zoomed}{}

=Observations
* Topics could be named
** Certain words indicate a focus on
*** Maintenance
*** Bug Fixing
*** Portability
*** Potential 'ilities

=Observations
* Powerlaw distribution of repeating topic counts
** Most occured once
** A few were repeated 
*** less than 10\% of topics reoccur

=Unfinished
* Total Topics versus Monthly Topics

=Future work
* Extension, associate Trends or Topics with purpoes by using wordnet and Taxonomies of software quality
